---
title: "State-wise ComComparison of crops  Productivity (2016 to 2018)"
author: "Ankit Varma"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
``## markdown
```{r}
library(readr)
library(dplyr) 
library(tidyr) 
library(stringr)
library(ggplot2)
Project_Combine <- read_csv("Project_1.xlsx - combined_ankit.csv")
View(Project_Combine)
```



# Filtering out data into different years 
```{r}
year_2016 <- filter( Project_Combine, years == 2016)

year_2017 <- filter(Project_Combine, years == 2017)

year_2018 <- filter(Project_Combine, years == 2018)
```



## Grouping the states into regions 
## Create a new column called 'region' based on the state name

```{r}
region_11 <- Project_Combine %>%
  mutate(region = case_when(
    states_uts %in% c("JAMMU & KASHMIR", "HIMACHAL PRADESH", "PUNJAB", "HARYANA", "RAJASTHAN","UTTARAKHAND") ~ "Northern",
    states_uts %in% c( "UTTAR PRADESH", "BIHAR", "JHARKHAND", "ODISHA", "WEST BENGAL","CHHATTISGARH") ~ "Eastern",
    states_uts %in% c("ANDHRA PRADESH", "KARNATAKA", "KERALA", "TAMIL NADU", "TELANGANA") ~ "Southern",
    states_uts %in% c("GUJARAT", "MAHARASHTRA") ~ "Western",
    states_uts %in% c("ARUNACHAL  PRADESH","ASSAM", "MIZORAM", "NAGALAND","SIKKIM", "MEGHALAYA", "MANIPUR", "TRIPURA" ) ~ "North-Eastern",
    TRUE ~ "Other"
  ))

```

## Group the data by region and summarize the mean production
```{r}
mean <- region_11 %>%
  group_by(region) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))
unique(region_11$region)

```


# Filtering individual crops data

```{r}
grapes<- filter(region_11, crops_name == 'grapes')

guava <- filter(region_11, crops_name == 'guava')

mango <- filter(region_11, crops_name == 'mango')

papaya <- filter(region_11, crops_name == 'papaya')

pineappple <- filter(region_11, crops_name == 'pineappple')

```

# Numerical Summary 

## Dimensions of the dataset tables 
```{r}
dim(Project_Combine)
dim(region_11)

```
```{r}
dim(region_11) 

```
<br>

## Mean productivity of each region

```{r}
region_11 %>%
  group_by(region) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))


```

## Mean productivity of each state

```{r}
region_11 %>%
  group_by(states_uts) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))


```

## Mean productivity of each year
```{r}
region_11 %>%
  group_by(years) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))
```

## Mean productivity of each crop

```{r}
region_11 %>%
  group_by(crops_name) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))
```

# Filtering individual crops data

```{r}
grapes<- filter(region_11, crops_name == 'grapes')

guava <- filter(region_11, crops_name == 'guava')

mango <- filter(region_11, crops_name == 'mango')

papaya <- filter(region_11, crops_name == 'papaya')

pineappple <- filter(region_11, crops_name == 'pineappple')
```


# Plotting individual crops data 


  
  ## Plotting data of grapes for all years 
  
```{r}
g9 <- ggplot(grapes , aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g9 + ggtitle("Productivity of Grapes regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))
```
  
   ## Plotting data of Guava for all years
```{r}
g10 <- ggplot(guava , aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g10 + ggtitle("Productivity of Guava regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))
```
   
    ## Plotting data of mango for all years 
```{r}
g11 <- ggplot(mango , aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g11 + ggtitle("Productivity of mango regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))
```
    
    ## Plotting data of papaya for all years 
```{r}
g12 <- ggplot(papaya, aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g12 + ggtitle("Productivity of papayaregionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))

```
    
    ## Plotting data of pineapple for all years
```{r}
g13 <- ggplot(pineappple, aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g13 + ggtitle("Productivity of pineapple regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))
```
   
## Combined crops plot

 ## Plotting a Jitter graph for the whole data
 
```{r}
g1 <- ggplot(Project_Combine, aes(crops_name, productivity_mt_ha, color = states_uts))
g1+ geom_jitter()
```
 
     ## Plotting a bar graph for the whole data
     
```{r}
g2 <- ggplot(Project_Combine, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))+ geom_col()
g2+ ggtitle( "States and there productivity for all crops (2016-2018)") +
  xlab( "Productivity in Metric ton/Hectare  ") +
  ylab(" States ")

```
     
       ## Plotting bar graph for the data of all crops only for 2016 year
```{r}
g3 <- ggplot(year_2016, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))
g3 + geom_col()
```

      ## Plotting bar graph for the data of all crops only for 2017 year
      
```{r}
g4 <- ggplot(year_2017, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))
g4 + geom_col()
```
    
      ## Plotting bar graph for the data of all crops only for 2018 year
```{r}
g5 <- ggplot(year_2018, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))
g5 + geom_col()
```
  
    ## Plotting bar graph of the data from new column region and Productivity Mt/Ha 
```{r}
g6 <- ggplot(region_11, aes(region, productivity_mt_ha, color = crops_name, fill = crops_name)) + geom_col()
g6+ ggtitle( "Region and there productivity for all crops (2016-2018)") +
  xlab( "States ") +
  ylab(" Productivity in Metric ton/Hectare  ")
```
    
      ## Plotting all crops data for each year 
```{r}
g7 <- ggplot(Project_Combine, aes(years, productivity_mt_ha, color = crops_name, fill = crops_name)) + geom_col()
g7+ ggtitle( "Productivity of all crops (2016-2018)") +
  xlab( " Year ") +
  ylab(" Productivity in Metric ton/Hectare  ")
```
  ## Append
  
  
library(readr)
library(dplyr) 
library(tidyr) 
library(stringr)
library(ggplot2)
Project_Combine <- read_csv("Project_1.xlsx - combined_ankit.csv")
View(Project_Combine)

unique(Project_Combine$crops_name)

# Filtering out data into different years 
year_2016 <- filter( Project_Combine, years == 2016)

year_2017 <- filter(Project_Combine, years == 2017)

year_2018 <- filter(Project_Combine, years == 2018)




## Grouping the states into regions 
## Create a new column called 'region' based on the state name

region_11 <- Project_Combine %>%
  mutate(region = case_when(
    states_uts %in% c("JAMMU & KASHMIR", "HIMACHAL PRADESH", "PUNJAB", "HARYANA", "RAJASTHAN","UTTARAKHAND") ~ "Northern",
    states_uts %in% c( "UTTAR PRADESH", "BIHAR", "JHARKHAND", "ODISHA", "WEST BENGAL","CHHATTISGARH") ~ "Eastern",
    states_uts %in% c("ANDHRA PRADESH", "KARNATAKA", "KERALA", "TAMIL NADU", "TELANGANA") ~ "Southern",
    states_uts %in% c("GUJARAT", "MAHARASHTRA") ~ "Western",
    states_uts %in% c("ARUNACHAL  PRADESH","ASSAM", "MIZORAM", "NAGALAND","SIKKIM", "MEGHALAYA", "MANIPUR", "TRIPURA" ) ~ "North-Eastern",
    TRUE ~ "Other"
  ))


## Group the data by region and summarize the mean production

mean <- region_11 %>%
  group_by(region) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))
unique(region_11$region)


## Mean productivity of each state

region_11 %>%
  group_by(states_uts) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))



  ## Mean productivity of each year
  
 
region_11 %>%
  group_by(years) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))


  
  ## Mean productivity of each crop
 
region_11 %>%
  group_by(crops_name) %>%
  summarize(mean_productivity_mt_ha = mean(`productivity_mt_ha`, na.rm = TRUE))




# Filtering individual crops data


grapes<- filter(region_11, crops_name == 'grapes')

guava <- filter(region_11, crops_name == 'guava')

mango <- filter(region_11, crops_name == 'mango')

papaya <- filter(region_11, crops_name == 'papaya')

pineappple <- filter(region_11, crops_name == 'pineappple')


# Plotting individual crops data 


  
  ## Plotting data of Cumin for all years 
  
g9 <- ggplot(grapes , aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g9 + ggtitle("Productivity of Grapes regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))




  
  
  ## Plotting data of Garilic for all years 
  
g10 <- ggplot(guava , aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g10 + ggtitle("Productivity of Guava regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))




  
  
  ## Plotting data of Ginger for all years 
 
g11 <- ggplot(mango , aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g11 + ggtitle("Productivity of mango regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))






  
  
  ## Plotting data of Tamarind for all years 
  
g12 <- ggplot(papaya, aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g12 + ggtitle("Productivity of papayaregionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))



  
  
  ## Plotting data of Turmeric for all years
 
g13 <- ggplot(pineappple, aes(states_uts, productivity_mt_ha))+ geom_col( color = 'blue', fill = 'blue')
g13 + ggtitle("Productivity of pineapple regionwise (2016-2018)") +
  xlab( " States ") +
  ylab(" Productivity in Metric ton/Hectare ")+ theme(axis.text.x = element_text(angle = 90, hjust = 0,vjust=0.5))


  
  ## Plotting a Jitter graph for the whole data
  
  
  
g1 <- ggplot(Project_Combine, aes(crops_name, productivity_mt_ha, color = states_uts))
g1+ geom_jitter()




  
  ## Plotting a bar graph for the whole data
  
  


g2 <- ggplot(Project_Combine, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))+ geom_col()
g2+ ggtitle( "States and there productivity for all crops (2016-2018)") +
  xlab( "Productivity in Metric ton/Hectare  ") +
  ylab(" States ")


  
  ## Plotting bar graph for the data of all crops only for 2016 year

g3 <- ggplot(year_2016, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))
g3 + geom_col()



  
  ## Plotting bar graph for the data of all crops only for 2017 year
  
 
g4 <- ggplot(year_2017, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))
g4 + geom_col()




  
  ## Plotting bar graph for the data of all crops only for 2018 year

g5 <- ggplot(year_2018, aes(productivity_mt_ha, states_uts, color = crops_name, fill = crops_name))
g5 + geom_col()


  
  ## Plotting bar graph of the data from new column region and Productivity Mt/Ha 


g6 <- ggplot(region_11, aes(region, productivity_mt_ha, color = crops_name, fill = crops_name)) + geom_col()
g6+ ggtitle( "Region and there productivity for all crops (2016-2018)") +
  xlab( "States ") +
  ylab(" Productivity in Metric ton/Hectare  ")



  
  ## Plotting all crops data for each year 
 
g7 <- ggplot(Project_Combine, aes(years, productivity_mt_ha, color = crops_name, fill = crops_name)) + geom_col()
g7+ ggtitle( "Productivity of all crops (2016-2018)") +
  xlab( " Year ") +
  ylab(" Productivity in Metric ton/Hectare  ")



  
  ## Plotting facet_wrap graph of Productivity of all crops for each year and grouped in region 
  

g8 <- ggplot(region_11, aes(years, productivity_mt_ha, color = crops_name, fill = crops_name)) + geom_col()+ facet_wrap(~region)
g8 + ggtitle( "Productivity of crops regionwise (2016-2018)") +
  xlab( " Year ") +
  ylab(" Productivity in Metric ton/Hectare ")


  
  
    